%% (Master) Thesis template
% Template version used: v1.4
%
% Largely adapted from Adrian Nievergelt's template for the ADPS
% (lecture notes) project.



%% We use the memoir class because it offers a many easy to use features.
\documentclass[11pt,a4paper,titlepage]{memoir}

%% Packages
%% ========

% for revision
\usepackage{float}
%% LaTeX Font encoding -- DO NOT CHANGE
\usepackage[OT1]{fontenc}

%% Babel provides support for languages.  'english' uses British
%% English hyphenation and text snippets like "Figure" and
%% "Theorem". Use the option 'ngerman' if your document is in German.
%% Use 'american' for American English.  Note that if you change this,
%% the next LaTeX run may show spurious errors.  Simply run it again.
%% If they persist, remove the .aux file and try again.
\usepackage[american]{babel}

%% Input encoding 'utf8'. In some cases you might need 'utf8x' for
%% extra symbols. Not all editors, especially on Windows, are UTF-8
%% capable, so you may want to use 'latin1' instead.
\usepackage[utf8]{inputenc}

%% This changes default fonts for both text and math mode to use Herman Zapfs
%% excellent Palatino font.  Do not change this.
\usepackage[sc]{mathpazo}

%% The AMS-LaTeX extensions for mathematical typesetting.  Do not
%% remove.
\usepackage{amsmath,amssymb,amsfonts,mathrsfs}

%% NTheorem is a reimplementation of the AMS Theorem package. This
%% will allow us to typeset theorems like examples, proofs and
%% similar.  Do not remove.
%% NOTE: Must be loaded AFTER amsmath, or the \qed placement will
%% break
\usepackage[amsmath,thmmarks]{ntheorem}

%% LaTeX' own graphics handling
\usepackage{graphicx}

%% We unfortunately need this for the Rules chapter.  Remove it
%% afterwards; or at least NEVER use its underlining features.
\usepackage{soul}

%% This allows you to add .pdf files. It is used to add the
%% declaration of originality.
\usepackage{pdfpages}

%% Some more packages that you may want to use.  Have a look at the
%% file, and consult the package docs for each.
\input{extrapackages}

%% Our layout configuration.  DO NOT CHANGE.
\input{layoutsetup}

%% Theorem environments.  You will have to adapt this for a German
%% thesis.
\input{theoremsetup}

%% Helpful macros.
\input{macrosetup}

%% Make document internal hyperlinks wherever possible. (TOC, references)
%% This MUST be loaded after varioref, which is loaded in 'extrapackages'
%% above.  We just load it last to be safe.
\usepackage[linkcolor=black,colorlinks=true,citecolor=black,filecolor=black]{hyperref}

\usepackage[export]{adjustbox}


\usepackage{subfig}
\usepackage{placeins}
\usepackage{scalerel}



%% Document information
%% ====================

\title{Two-Neutron Correlations in the Photofission of Actinides}
\author{Jeffrey S. Burggraf}
\thesistype{phd Thesis}
\advisors{Advisors: Prof.\ Dr.\ D. S. Dale}
\department{Department of Physics}
\date{January 19, 2018}

% double spacing for comments. 
\DisemulatePackage{setspace}
\usepackage{setspace} 
\setstretch{1.75}
\usepackage[margin=1.5in]{geometry}
\usepackage[inline]{enumitem}
\usepackage{xcolor}
\usepackage[textsize=small]{todonotes}
%
\setlength{\marginparwidth}{2.5cm}

\begin{document}

\frontmatter

%% Title page is autogenerated from document information above.  DO
%% NOT CHANGE.
\begin{titlingpage}
  \calccentering{\unitlength}
  \begin{adjustwidth*}{\unitlength-24pt}{-\unitlength-24pt}
    \maketitle
  \end{adjustwidth*}
\end{titlingpage}

%% The abstract of your thesis.  Edit the file as needed.
\input{abstract}

%% TOC with the proper setup, do not change.
\cleartorecto
\tableofcontents
\mainmatter


\input{Content/Introduction/Introduction.tex}
\input{Content/Methods/Methods.tex}
\input{Content/Errors/Errors.tex}
\input{Content/Results/Results.tex}


\chapter{Concluding Remarks}
% TODO: Make this section complete. 
Two-neutron angular correlations in the photofission of $^{238}$U were measured using 10.5 MeV end-point bremsstrahlung photons produced via a low duty factor, pulsed linear electron accelerator.
The measured angular correlations reflect the underlying back-to-back nature of the fission fragments.
The method of analysis uses a single set of experimental data to produce a opening angle distribution of correlated and uncorrelated neutron pairs.
A ratio is taken between these two sets to provide a self-contained result of angular correlations that is independent of neutron detector efficiencies.
Two-neutron angular correlation measurements were also made using neutrons from the SF of $^{252}$Cf and are in good agreement with previous measurements.

Measured two-neutron opening angular correlations were in fair agreement with simulations that used FREYA version 2.0.3, which uses a neutron-induced model to approximate photofission.
These data will be useful for fine-tuning the photofission models that will be incorporated into future versions of FREYA.

An anomaly was observed in the rate of neutron emission at opening angles near 180$^{\circ}$, in which diminished rates resulted in a local maximum at about 160$^{\circ}$ instead of the expected 180$^{\circ}$ as seen in all past measurements of neutron-induced and spontaneous fission.
We offer two possible explanations for this effect:
\begin{enumerate*}[label=(\roman*), itemjoin={{, }}, itemjoin*={{, or }}]
  \item There is a decrease in neutron emission along the fission axis
  \item the neutrons may indeed be emitted isotropically in the rest frame of the fission fragment, but one fragment essentially shadows the neutrons emitted from the other fragment, either through absorption or scattering.
  \end{enumerate*}
A definitive interpretation of this decreased two-neutron correlation for large opening angles in photo-fission requires further study.

\appendix

\input{appendix}

\backmatter

\bibliographystyle{plain}
\bibliography{./refs.bib}


\end{document}